Thesis_R_Code

### 2023-04-20 code/Thesis_R_Code.Rmd
saved r code

summary(arma_model)
residuals_garch <- residuals(garch_model)
plot(residuals_garch)
```

## Adding Exogenous Variable (sentiment score)
```{r}
sentiment_df <- read.csv("/Users/pranavtavildar/Desktop/Senior-Thesis/data/daily_sentiments.csv", header = TRUE)
str(sentiment_df)
str(returns)
sentiment_df = sentiment_df[-1,]
hist(sentiment_df$sentiment, main = "Sentiment Distribution", xlab = "Sentiment Score", ylab = "Frequency")

output_path <- "/Users/pranavtavildar/Desktop/Senior-Thesis/FrontiersPoster/FrontiersPoster_files/poster_files/figures/sentimenthist.png"

>>>>

summary(arma_model)
output_path <- "/Users/pranavtavildar/Desktop/Senior-Thesis/figures/fig4.pdf"

pdf(file = output_path)
residuals_garch <- residuals(garch_model)
plot(residuals_garch)
```

## Adding Exogenous Variable (sentiment score)
```{r}
sentiment_df <- read.csv("/Users/pranavtavildar/Desktop/Senior-Thesis/data/daily_sentiments.csv", header = TRUE)
str(sentiment_df)
str(returns)
sentiment_df = sentiment_df[-1,]

output_path <- "/Users/pranavtavildar/Desktop/Senior-Thesis/figures/fig3.pdf"

pdf(file = output_path)
hist(sentiment_df$sentiment, main = "Sentiment Distribution", xlab = "Sentiment Score", ylab = "Frequency")
dev.off()
